title TBD

### 2016-01-11 SC-challenge.tex
adding some intro thoughts

\acmformat{Kyle E. Niemeyer, Arfon M.\ Smith, and Daniel M.\ Katz, 2016. Title TBD.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

@@

Author's addresses: K. E. Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University; 
A. M. Smith,
GitHub, Inc.; 
D. M. Katz,
Computation Institute, University of Chicago \& Argonne National Laboratory.
\end{bottomstuff}

@@

@@

>>>>

\acmformat{Kyle E.\ Niemeyer, Arfon M.\ Smith, and Daniel S.\ Katz, 2016. Title TBD.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

@@

Some work by D.\ S.\ Katz was supported by the National Science Foundation (NSF) while working at the Foundation; any opinion, finding, and conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the NSF.

Author's addresses: K.\ E.\ Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University; 
A.\ M.\ Smith,
GitHub, Inc.; 
D.\ S.\ Katz,
Computation Institute, University of Chicago \& Argonne National Laboratory.
\end{bottomstuff}

@@

Software is important in science.

But academic credit and reputation are generally based on publications.

To increase the amount of software developed and shared, we can consider how we might
treat software as if it was a publication.

This means we need a way to uniquely identify released (published) software so that it can be cited by others who use it, and we need a process for peer review for software. Here, we focus on the former.

@@

Project CREDiT
